Measuring neutron star tidal deformability with Advanced LIGO: a Bayesian analysis of neutron star - black hole binary observations

### 2017-01-18 Paper/journal_submission/paper.tex
resubmitted

% ###########################################################
% ###########################################################
\section{Choice of underlying BBH model in LEA}
% ###########################################################
% 
\begin{figure}
\centering    
\includegraphics[width=1.05\columnwidth]{match-q-spin1-PhenomC-mf0_01.pdf}
\caption{%
We compare two alternatives of the tidal NSBH model from Ref.~\cite{
Lackey:2013axa}, which differ in their underlying BBH prescriptions. One which
we use in this study uses SEOBNRv2, while the other uses IMRPhenomC as its
base. In this figure, we show the normalized overlap (match) between the two for
$2,000,000$ points sampled uniformly in the NSBH parameter space. We find that
for $q\gtrsim 4$ the discrepancies between IMRPhenomC and SEOBNRv2 as reported
in~\cite{Kumar:2015tha} dominate over tidal terms.
\label{fig:PhenomC_vs_SEOBNRv2_LEA}
}
\end{figure}
%
The waveform model used in this paper is a variant of those calibrated
in Ref~\cite{Lackey:2013axa}. In that work, the authors also calibrate
a tidal prescription with the phenomenological model IMRPhenomC~\cite{
Santamaria:2010yb}
as the base BBH model. Previous work~\cite{Kumar:2015tha,Kumar:2016dhh} has 
shown that IMRPhenomC can exhibit pathological behavior for mass-ratios
$q\gtrsim 4$ and/or non-zero black hole spins. We compute noise-weighted
inner-products between the two variants for $2,000,000$ points sampled
over the NSBH parameter space, and show the results in 
Fig.~\ref{fig:PhenomC_vs_SEOBNRv2_LEA}. We restrict the comparison to frequencies
that are affected by the tidal disruption of the NS, by integrating
the inner-products from $f = \mathrm{max}(15, 0.01/M)$~Hz
(where $M$ is expressed in seconds ($1M_\odot \simeq 4.925\mu$S, see
Eq.~(32-34) of~\cite{Lackey:2013axa}).
% 
We find that the differences between the two BBH approximants cause mismatches
of a few percent, while the tidal corrections contribute at a sub-percent
level. We conclude that the differences of the underlying BBH model in LEA+
dominates over their tidal calibration, and since SEOBNRv2 has been shown to
be more reliable than IMRPhenomC~\cite{Kumar:2015tha,Kumar:2016dhh}, we 
recommend the use of SEOBNRv2-based LEA+ in upcoming LIGO-Virgo analyses.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{References}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{References}

>>>>

% ###########################################################
% ###########################################################
\section{Choice of underlying BBH model in LEA}
% ###########################################################
% 
\begin{figure}
\centering    
\includegraphics[width=1.05\columnwidth]{match-q-spin1-PhenomC-mf0_01.pdf}
\caption{%
We compare two alternatives of the tidal NSBH model from Ref.~\cite{
Lackey:2013axa}, which differ in their underlying BBH prescriptions. One which
we use in this study uses SEOBNRv2, while the other uses IMRPhenomC as its
base. In this figure, we show the normalized overlap (match) between the two for
$2,000,000$ points sampled uniformly in the NSBH parameter space. We find that
for $q\gtrsim 4$ the discrepancies between IMRPhenomC and SEOBNRv2 as reported
in~\cite{Kumar:2015tha} dominate over tidal terms.
\label{fig:PhenomC_vs_SEOBNRv2_LEA}
}
\end{figure}
%
The waveform model used in this paper is a variant of those calibrated
in Ref~\cite{Lackey:2013axa}. In that work, the authors also calibrate
a tidal prescription with the phenomenological model IMRPhenomC~\cite{
Santamaria:2010yb}
as the base BBH model. Previous work~\cite{Kumar:2015tha,Kumar:2016dhh} has 
shown that IMRPhenomC can exhibit pathological behavior for mass-ratios
$q\gtrsim 4$ and/or non-zero black hole spins. We compute noise-weighted
inner-products between the two variants for $2,000,000$ points sampled
over the NSBH parameter space, and show the results in 
Fig.~\ref{fig:PhenomC_vs_SEOBNRv2_LEA}. We restrict the comparison to frequencies
that are affected by the tidal disruption of the NS, by integrating
the inner-products from $f = \mathrm{max}(15, 0.01/M)$~Hz
(where $M$ is expressed in seconds ($1M_\odot \simeq 4.925\mu$S, see
Eq.~(32-34) of~\cite{Lackey:2013axa}).
% 
We find that the differences between the two variants of LEA+ have mismatches
of a few percent, while the tidal corrections contribute at a sub-percent
level. We conclude that the differences of the underlying BBH model in LEA+
dominate over its tidal calibration, and since SEOBNRv2 has been shown to
be more reliable than IMRPhenomC~\cite{Kumar:2015tha,Kumar:2016dhh}, we 
recommend the use of SEOBNRv2-based LEA+ in upcoming LIGO-Virgo analyses.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{References}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{paper}
